---
output: github_document
--- 
cefiro
======

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

<!-- badges: start -->
[![](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- badges: end -->

Package allows carry out simple calculations and plots for wind measurement data.

### Installation

Get the development version 0.0.9000 from github:

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("prcwiek/cefiro")
```

```{r}
library('cefiro')
```

### Contributors and wind measurement data example

Wind measurement data example was extracted from US Virgin Islands, St. Thomas Bovoni mast 
https://midcdmz.nrel.gov/apps/sitehome.pl?site=USVILONA  
  
Roberts, O.; Andreas, A.; (1997). United States Virgin Islands:  
St. Thomas & St. Croix (Data); NREL Report No. DA-5500-64451.  
http://dx.doi.org/10.7799/1183464  



