---
output: github_document
--- 
cefiro
======

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

<!-- badges: start -->
[![CRAN](https://www.r-pkg.org/badges/version/cefiro)](https://cran.r-project.org/package=cefiro)
[![](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- badges: end -->

Package allows carry out simple calculations and plots for wind measurement data.

### Installation

Get the development version 0.0.9007 from github:

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("prcwiek/cefiro")
```

```{r}
library('cefiro')
```

### Contributors and wind measurement data example

Wind measurement data example was extracted from 
Wind resource data from the tall Risø met mast.
  
Hansen, Kurt Schaldemose; Vasiljevic, Nikola; Sørensen, Steen Arne (2021). 
Wind resource data from the tall Risø met mast. Technical University of Denmark. Dataset.
https://doi.org/10.11583/DTU.14153204.v1

https://doi.org/10.11583/DTU.14153204.v1



