---
title: "Working with cefiro package"
author: "Pawel Cwiek"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
  chunk_output_type: inline
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Package cefiro

Cefiro is an R package that allows to carry out simple calculations and
creat simple graphs for wind measurement data.

## Example wind measurement data

Wind measurement data example was extracted from 
Wind resource data from the tall Risø met mast.
  
Hansen, Kurt Schaldemose; Vasiljevic, Nikola; Sørensen, Steen Arne (2021). 
Wind resource data from the tall Risø met mast. Technical University of Denmark. Dataset.
<https://doi.org/10.11583/DTU.14153204.v1>

<https://doi.org/10.11583/DTU.14153204.v1>


```{r example wind measurement data}
library(cefiro)
library(dplyr, warn.conflicts = FALSE)
library(gt)
library(RColorBrewer)
```

```{r look_at_data}
knitr::kable(head(winddata))
```

## Creating a c_mseries object from wind measurement data

First, we have to create a c_mseries object. The example data set
consist of the following signals

```{r signals in wind measurement data}
names(winddata)
```

For each 10 minutes there are:

-   wind speeds at 125 m, 77 m and 44 m
-   wind directions at 77 m and 125 m
-   temperature at 3 m, 44 m and 118 m
-   pressure at 8 m

Let's create a c_mseries object

```{r creating c_mseries}
dm <- c_mseries(mdata = winddata, date_col = "DateTime",
                ws_col = c("WS125", "WS77", "WS44"), ws_h = c(125, 77, 44),
                dir_col = c("WD77", "WD125"), dir_h = c(77, 125),
                t_col = c("T3", "T44", "T118"), t_h = c(3, 44, 118),
                p_col = "P8", p_h = 8,
                name = "Test_mast",
                tzone = "CET")
```

We can check dm

```{r checking dm}
dm
```

For now the main wind speed sensor is named WS125 and the main direction
sensor is WD125.

## Summary of c_mseries objects
```{r summary}
summary(dm)
```


## Mean, median, maximum and minimum vales

Mean of the main wind speed sensor

```{r mean main}
mean(dm)
```

and for other sensors

```{r mean others}
mean(dm, signal = "WS77")
mean(dm, signal = "T118")
```

The same we can do with median, max and min functions and for other
sensors

```{r median, min, max}
median(dm, signal = "WS77")
max(dm, signal = "WS77")
min(dm, signal = "WS77")
```

## Time series plots

Let's plot time series for main signals

```{r first plots, fig.show='hold', fig.width=6}
plot(dm)
plot(dm, signal = "WD125", col = "#E69F00")
plot(dm, signal = "T118")
plot(dm, signal = "P8")
```

Temperature for July 1999

```{r second plots, fig.show='hold', fig.width=6}
plot(dm, signal = "T118", start_date = "1999-07-01", end_date = "1999-07-31", col = "red")
```

Pressure for 3 May 1999

```{r third plots, fig.show='hold', fig.width=6}
plot(dm, signal = "P8", start_date = "1999-05-03", end_date = "1999-05-03", col = "green")
```

Three signals at once

```{r fourth plots, fig.show='hold', fig.width=6}
plot(dm, signal = c("WS125", "WS77", "WS44"))
```

## Histogram plots

It is possible to create histograms for single levels

```{r histograms, fig.show='hold'}
hist(dm)
hist(dm, signal = "WD125", col = "#E69F00")
hist(dm, signal = "T118", col = "red")
hist(dm, signal = "P8", col = "green")
```

## Weibull distribution
It is possible to define a Weibull distribution as the c_weibull object
```{r weibull1}
c_weibull(c = 7.0, k = 1.8, ws = 5.0, ro = 1.225)
```
or
```{r weibull2}
distribution_example <- c_weibull(c = 7.0, k = 1.8, ws = 5.0, ro = 1.225)
```
A plot or a histogram can be generated
``` {r weibull3, fig.show='hold'}
plot(distribution_example, col = "red", lwd = 2)
hist(distribution_example)
```

## Finding the scale c factor and the shape k factor of the Weibull distribution
With the created above c_mseries it is possible to find c and k values.
```{r finding_Weibull}
c_find_weibull(dm)
c_find_weibull(dm, signal = "WS77")
```

## Ploting wind roses
Function c_windrose allows to plot wind roses from maximum two wind directions sensors
```{r wind_rose, fig.width=6}
c_windrose(dm)
c_windrose(dm, signal = c("WD77", "WD125"))
```

## Plotting Weibull distribution and histogram
Function c_weibull_plot allows to plot Weibull distribution in
the different way.
```{r weibull_plots, fig.width=6}
c_weibull_plot(dm)
c_weibull_plot(dm, hist =TRUE)
c_weibull_plot(dm, line = FALSE, hist =TRUE)
c_weibull_plot(c = 7.0, k = 2.0, vmin = 0, vmax = 25, lcolor = "red", lsize = 1, hist = TRUE, hcolor = "orange")
```

## Means and means of monthly means
For finding means of each month of measurements we can use the function c_means
```{r means}
c_means(dm) |>
  gt() |>
  data_color(method = "numeric",
             columns = c("WS125", "WS77", "WS44"),
             palette = "Spectral",
             reverse = TRUE)
```
Also it is posible to calculate means of monthly means.
```{r mom}
c_means(dm, mom = TRUE) |>
  gt() |>
  data_color(method = "numeric",
             columns = c("WS125", "WS77", "WS44"),
             palette = "Spectral",
             reverse = TRUE)
```

### More soon...
